\documentclass[10pt]{article}

\usepackage[a4paper,top=2.0cm,bottom=2.0cm,left=1.4cm,right=1.4cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{ragged2e}

\definecolor{sapphire}{rgb}{0.03, 0.15, 0.40}
\hypersetup{
  colorlinks=true,
  urlcolor=sapphire,
  linkcolor=sapphire
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\setlist[itemize]{topsep=0.15em,itemsep=0.2em,leftmargin=1.3em}

\long\def\cvsection#1#2{%
  \noindent
  \begin{minipage}[t]{0.13\textwidth}
  {\small\scshape #1}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.83\textwidth}
  #2
  \end{minipage}\par\vspace{0.8em}
}

\begin{document}

{\LARGE\bfseries Houssam Zenati}\hfill
\begin{tabular}[t]{r}
\href{mailto:h.zenati@ucl.ac.uk}{h.zenati@ucl.ac.uk} \\
\href{https://orcid.org/0009-0001-7682-8459}{ORCID: 0009-0001-7682-8459} \\
\href{https://houssamzenati.github.io}{https://houssamzenati.github.io}
\end{tabular}

\vspace{0.15em}
25 Howland St, London W1T 4JG, United Kingdom

\vspace{0.2em}
\hrule
\vspace{0.9em}

\cvsection{Research Interests}{
Statistical and algorithmic questions in machine learning systems, especially sequential decision-making, policy learning, causal inference, nuisance-robust methods, and inference under adaptive data collection.
}

\cvsection{Professional\\Experience}{
{\bfseries Gatsby Computational Neuroscience Unit, University College London}, United Kingdom\\
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textit{Research Fellow} & 2025--present \\
\end{tabularx}
Developing methods for semiparametric efficient distributional causal inference, adaptive data collection, and sequential decision-making.

\vspace{0.6em}

{\bfseries INRIA MIND / PreMeDical}, France\\
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textit{Postdoctoral Researcher} & 2023--2024 \\
\end{tabularx}
Research on causal inference and mediation analysis, including double machine learning estimators and open-source software development.

\vspace{0.6em}

{\bfseries Criteo AI Lab}, France\\
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textit{PhD Researcher} & 2020--2023 \\
\textit{Research Engineer} & 2019--2020 \\
\end{tabularx}
Worked on counterfactual policy learning and online/bandit problems, including optimization methods, contextual bandits, and kernel methods.

\vspace{0.6em}

{\bfseries Institute for Infocomm Research (A\*STAR)}, Singapore\\
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textit{Research Intern / Research Experience} & 2017--2018 \\
\end{tabularx}
Worked on deep representation learning, generative adversarial networks, anomaly detection, and semi-supervised learning, with applications to medical imaging.
}

\cvsection{Education}{
{\bfseries Universit\'e Grenoble Alpes / INRIA Thoth}, France \hfill 2023\\
Ph.D.\ in applied mathematics and machine learning.\\
Thesis: \textit{Efficient Methods in Counterfactual Policy Learning and Sequential Decision Making}.

\vspace{0.6em}

{\bfseries ENS Paris-Saclay / MVA}, France \hfill 2019\\
M.Sc.\ in mathematics, vision, and learning.

\vspace{0.4em}

{\bfseries CentraleSup\'elec}, France \hfill 2015--2019\\
M.Eng.\ in applied mathematics and computer science.
}

\cvsection{Selected\\Publications}{
S. Girard, A. Bibaut, A. Gretton, N. Kallus, \textbf{H. Zenati} (2026). \textit{Fast Best-in-Class Regret for Contextual Bandits}. UAI.\\
\href{https://arxiv.org/abs/2510.15483}{arXiv:2510.15483}

\vspace{0.5em}

Z. Shen, \textbf{H. Zenati}, N. Kallus, A. Gretton, K. Khamaru, A. Bibaut (2026). \textit{Efficient Inference after Directionally Stable Adaptive Experiments}. Preprint.\\
\href{https://arxiv.org/abs/2602.21478}{arXiv:2602.21478}

\vspace{0.5em}

\textbf{H. Zenati}, B. Bozkurt, A. Gretton (2025). \textit{Doubly-Robust Estimation of Counterfactual Policy Mean Embeddings}. NeurIPS.

\vspace{0.5em}

\textbf{H. Zenati}, E. Diemert, M. Martin, J. Mairal, P. Gaillard (2023). \textit{Sequential Counterfactual Risk Minimization}. ICML.

\vspace{0.5em}

\textbf{H. Zenati}, A. Bietti, E. Diemert, J. Mairal, M. Martin, P. Gaillard (2022). \textit{Efficient Kernelized UCB for Contextual Bandits}. AISTATS.
}

\newpage

\cvsection{Other\\Publications}{
\textbf{H. Zenati}, B. Bozkurt, A. Gretton (2026). \textit{Kernel Treatment Effects with Adaptively Collected Data}. AISTATS.

\vspace{0.4em}

F. El Khoury*, \textbf{H. Zenati}*, N. Kallus, M. Arbel, A. Bibaut (2026). \textit{Semiparametric Efficient Bilevel Gradient Estimation}. Preprint.

\vspace{0.4em}

B. Bozkurt, A. Galashov, D. Meunier, Z. Shen, A. Gretton, \textbf{H. Zenati} (2026). \textit{Doubly Robust Proxy Causal Learning with Neural Mean Embeddings}. Preprint.

\vspace{0.4em}

\textbf{H. Zenati}, A. Gretton (2026). \textit{Semiparametric Efficient Test for Interpretable Distributional Treatment Effects}. Preprint.

\vspace{0.4em}

A. Bibaut, \textbf{H. Zenati}, T. Rahier, N. Kallus (2026). \textit{Functional Natural Policy Gradients}. Preprint.

\vspace{0.4em}

Z. Shen, D. Meunier, \textbf{H. Zenati}, A. Gretton, N. Kallus, A. Bibaut (2026). \textit{Instrumental Variable Analysis Without Structural Equations}. Preprint.

\vspace{0.4em}

\textbf{H. Zenati}, J. Abecassis, J. Josse, B. Thirion (2025). \textit{Double Debiased Machine Learning for Mediation Analysis with Continuous Treatments}. AISTATS.

\vspace{0.4em}

J. Abecassis, \textbf{H. Zenati}, S. Boumaiza, J. Josse, B. Thirion (2025). \textit{Causal Mediation Analysis with One or Multiple Mediators: A Comparative Study}. Psychological Methods.

\vspace{0.4em}

B. Bozkurt, \textbf{H. Zenati}, D. Meunier, L. Xu, A. Gretton (2025). \textit{Density Ratio-Free Doubly Robust Proxy Causal Learning}. NeurIPS.

\vspace{0.4em}

\textbf{H. Zenati}, A. Bietti, M. Martin, E. Diemert, P. Gaillard, J. Mairal (2025). \textit{Counterfactual Learning of Stochastic Policies with Continuous Actions}. Transactions on Machine Learning Research.

\vspace{0.4em}

J. Zhou, P. Gaillard, T. Rahier, \textbf{H. Zenati}, J. Arbel (2024). \textit{Towards Efficient and Optimal Covariance-Adaptive Algorithms for Combinatorial Semi-Bandits}. NeurIPS.

\vspace{0.4em}

M. Martin, P. Mertikopoulos, T. Rahier, \textbf{H. Zenati} (2022). \textit{Nested Bandits}. ICML.

\vspace{0.4em}

\textbf{H. Zenati}, A. Bietti, M. Martin, E. Diemert, J. Mairal (2020). \textit{Optimization Approaches for Counterfactual Risk Minimization with Continuous Actions}. ICLR Workshop on Causal Learning for Decision Making.

\vspace{0.4em}

P. Mertikopoulos, B. Lecouat, \textbf{H. Zenati}, C.-S. Foo, V. Chandrasekhar, G. Piliouras (2019). \textit{Optimistic Mirror Descent in Saddle-Point Problems: Going the Extra (Gradient) Mile}. ICLR.

\vspace{0.4em}

K. Ouardini, H. Yang, B. Unnikrishnan, M. Romain, C. Garcin, \textbf{H. Zenati}, J. P. Campbell, M. F. Chiang, J. Kalpathy-Cramer, V. Chandrasekhar, et al. (2019). \textit{Towards Practical Unsupervised Anomaly Detection on Retinal Images}. MICCAI Workshop on Domain Adaptation and Representation Transfer.

\vspace{0.4em}

\textbf{H. Zenati}, M. Romain, C.-S. Foo, B. Lecouat, V. Chandrasekhar (2018). \textit{Adversarially Learned Anomaly Detection}. ICDM.

\vspace{0.4em}

\textbf{H. Zenati}, C.-S. Foo, B. Lecouat, G. Manek, V. R. Chandrasekhar (2018). \textit{Efficient GAN-Based Anomaly Detection}. ICLR Workshop.

\vspace{0.4em}

B. Lecouat, C.-S. Foo, \textbf{H. Zenati}, V. Chandrasekhar (2018). \textit{Semi-Supervised Learning with GANs: Revisiting Manifold Regularization}. ICLR Workshop.

\vspace{0.4em}

B. Lecouat, C.-S. Foo, \textbf{H. Zenati}, V. Chandrasekhar (2018). \textit{Manifold Regularization with GANs for Semi-Supervised Learning}. arXiv preprint.

\vspace{0.4em}

B. Lecouat, K. Chang, C.-S. Foo, B. Unnikrishnan, J. M. Brown, \textbf{H. Zenati}, A. Beers, V. Chandrasekhar, J. Kalpathy-Cramer, P. Krishnaswamy (2018). \textit{Semi-Supervised Deep Learning for Abnormality Classification in Retinal Images}. NeurIPS Workshop on Machine Learning for Health.
}

\cvsection{Teaching}{
{\bfseries Data Visualisation}, Universit\'e Paris Dauphine -- PSL \hfill 2021--2022\\
Instructor for Master's students in the IASD program. Covered visualisation as a statistical and algorithmic tool for exploring, summarizing, and communicating complex data, with topics including graphical principles and dimensionality-reduction methods such as PCA, multidimensional scaling, and t-SNE.

\vspace{0.4em}

{\bfseries Advanced Machine Learning}, CentraleSup\'elec \hfill 2024--2025\\
Teaching assistant alongside Emilie Chouzenoux. Helped students connect the formal ideas in modern machine learning, statistics, and optimization to practical algorithms and empirical behavior.

\vspace{0.4em}

{\bfseries Causal Inference}, New York University Paris \hfill 2024--2025\\
Co-instructor with Judith Abecassis. Taught lectures and recitations on randomized and observational causal inference, including identification assumptions, weighting, matching, instrumental variables, and regression discontinuity.

\vspace{0.6em}

Teaching philosophy: conceptual clarity, mathematical rigor, and active engagement.
}

\cvsection{Student\\Supervision}{
- Julien Zhou, Master's student \hfill 2023\\
- Samuel Girard, PhD student \hfill 2025--2026\\
- Robin Leman, Master's student \hfill 2026
}

\cvsection{Talks}{
- \textit{Doubly-Robust Estimation of Counterfactual Policy Mean Embeddings}, INRIA Thoth, France \hfill Oct.\ 2025\\
- \textit{Doubly-Robust Estimation of Counterfactual Policy Mean Embeddings}, Symposium on Mathematical Foundations of Trustworthy Learning, Switzerland \hfill Oct.\ 2025\\
- \textit{Sequential Counterfactual Risk Minimization}, ELLIS Unconference, France \hfill Jul.\ 2023\\
- \textit{Sequential Counterfactual Risk Minimization}, INRIA Lille, France \hfill Jun.\ 2023\\
- \textit{Nested Bandits}, ICML, United States \hfill Jul.\ 2022\\
- \textit{Efficient Kernelized Contextual Bandits}, virtual talk \hfill May 2022\\
- \textit{Optimization Approaches for Counterfactual Risk Minimization with Continuous Actions}, virtual talk \hfill Apr.\ 2020\\
- \textit{Adversarially Learned Anomaly Detection}, ICDM, Singapore \hfill Nov.\ 2018\\
- \textit{Efficient GAN-Based Anomaly Detection}, DL2.0 Workshop, I2R, A\*STAR, Singapore \hfill Apr.\ 2018
}

\cvsection{Service}{
{\bfseries Reviewing}\\
AISTATS, ICML, NeurIPS, ICLR, TMLR

\vspace{0.6em}

{\bfseries Reading Group Organization}\\
Co-organized a reading group at Gatsby, UCL on van der Vaart's \textit{Asymptotic Statistics} \hfill 2026\\
Organized a reading group at Inria Paris-Saclay on Wainwright's \textit{High-Dimensional Statistics} \hfill 2023--2024

\vspace{0.6em}

{\bfseries Workshop and Seminar Organization}\\
Advances on Adaptive Experimentation (AAE) Workshop, Gatsby Unit \hfill 2026\\
External machine learning seminars, Gatsby Unit, UCL \hfill since Sept.\ 2025
}

\cvsection{Software}{
\href{https://judithabk6.github.io/med_bench/}{\textbf{med\_bench}}: Python package for causal mediation analysis with a unified implementation of common estimators and flexible nuisance models.

\vspace{0.6em}

Open-source research code:

\vspace{0.2em}

\begin{itemize}
\item \href{https://github.com/houssamzenati/adaptive-KTE}{adaptive-KTE}
\item \href{https://github.com/houssamzenati/counterfactual-policy-mean-embedding}{counterfactual-policy-mean-embedding}
\item \href{https://github.com/houssamzenati/double-debiased-machine-learning-mediation-continuous-treatments}{double-debiased-machine-learning-mediation-continuous-treatments}
\item \href{https://github.com/criteo-research/sequential-counterfactual-risk-minimization}{sequential-counterfactual-risk-minimization}
\item \href{https://github.com/criteo-research/Efficient-Kernel-UCB}{Efficient-Kernel-UCB}
\item \href{https://github.com/criteo-research/Nested-Exponential-Weights}{Nested-Exponential-Weights}
\item \href{https://github.com/criteo-research/optimization-continuous-action-crm}{optimization-continuous-action-crm}
\item \href{https://github.com/houssamzenati/Adversarially-Learned-Anomaly-Detection}{Adversarially-Learned-Anomaly-Detection}
\item \href{https://github.com/houssamzenati/Efficient-GAN-Anomaly-Detection}{Efficient-GAN-Anomaly-Detection}
\end{itemize}
}

\end{document}
